The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-07-17 Stickleback_Paper.tex
abstract

Trait | Phenotype = Probably Trait

@@

should we be using the word ``patch"?

@@

\todo{Do last.}

@@

\todo{Take out any "we's" and be more specific}

>>>>

@@

\textbf{Pending things to do?} that maybe we do, maybe not

longer genomes ($10^8$ not $10^5$ but rescaling everything accordingly)

verify that adaptation of introduced pops is due to initial diversity not subsequent migration

@@

Ninespine stickleback provide one of the most striking examples of local adaptation,
as the hemisphere-wide metapopulation includes both marine populations
and a large number of smaller freshwater populations
that have apparently repeatedly adapted to freshwater conditions
often using the same genetic basis.
In this paper, we use simulations motivated by stickleback populations
to examine what amounts of gene flow favor stable metapopulation polymorphism
with allele sharing,
and to further dissect the underlying dynamics.
We find that rapid, repeated adaptation 
using alleles maintained at low frequency by migration-selection balance
(the ``transporter hypothesis'')
occurs over a realistic range of intermediate rates of gene flow,
between slow, independent adaptation with low gene flow
and large migration load at high gene flow.
We do not see evidence for strong effects encouraging genomic clustering of causal alleles
or towards particular dominance coefficients.
$F_{ST}$ scans for adaptive alleles are more likely to succeed with higher rates of gene flow,
The results support existing theory of local adaptation,
and provide a more concrete look at a particular, empirically motivated example.

@@
